---
title: My dynamic report
subtitle: How healthy do I eat?
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library(magick)
```

```{css}
body {
  color: #474954;
  background-color: #DFE9AC;
  font-family: monospace;
}

h1 {
  color: #F7FFF7;
  background-color: #1A895D;
  font-family: monospace;
  font-weight: bold;
  padding: 15px;
  font-size: 20px;
}

h2{
  color: #F7FFF7;
  background-color: #1A895D;
  font-family: monospace;
  font-weight: bold;
  padding: 3px;
  font-size: 15px;
```

# What's going on with this data?

Let's explore some summary statistics and make some graphs and see what we find out about my eating habits.

## Summary 1: What is the max amount of grams of protein?

```{r}
library(tidyverse)
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vSYdDVLpDF2qe3SjXviKt_gwCNLvyCnTGAPlllPGQm7SNkAUVX7jttBRFgBcYrOd7ujuUPRT0IXgklb/pub?output=csv")
latest_data <- logged_data %>% 
  select(-`Column 4`) %>% #remove column 4
  rename("Taste" = 2, #rename columns for easy read
         "Number_of_Fruit_Vege" = 3,
         "Grams_of_Protein" = 4,
         "Sweet_Savoury" = 5) 
max_protein <- max(latest_data$Grams_of_Protein) #max amount of protein
cat(max_protein)
```


## Summary 2: What is the average taste of a meal (stars 1-5)?


```{r}
#Summary 2
average_taste <- mean(latest_data$Taste) #average taste 
cat(average_taste)
```


## Graph 1: Sweet or Savoury?
```{r}
#Graph 1
latest_data %>%
  ggplot() +
  geom_bar(aes(y = Sweet_Savoury),
               fill = "#97BE11")+
  theme_minimal()+
  labs(title = "Overall count comparison of sweet and savoury meals", x = "Count", y = "Flavour Profile")
```

This plot shows the overall count comparison of sweet and savoury meals. The type of meal with the highest count was sweet at 12 meals. This indicates I consume more sweet meals than savoury.



## Graph 2: Overall taste rating of meals
```{r}
#Graph 2
ggplot(latest_data, aes(x = factor(Taste, levels = 1:5))) +
  geom_bar(fill = "#FFDA1F") +
  labs(x = "Taste Rating (1-5 stars)", y = "Count", title = "Overall Taste Rating of Meals") +
  theme_minimal() +
  scale_x_discrete(limits = as.character(1:5))
```

This plot shows the count of the rating of my meals out of 5 stars. The rating with the highest count was 5 stars where 15 of my meals I gave a 5 star rating.
